France-wide 10\,m Deciduous-Evergreen Map from Sentinel-2 Harmonic Features

### 2025-09-19 article/article_old.tex
fixed similarity analysis

\begin{table}[H]
    \centering
    \begin{tabular}{lccc}
        \hline
        \textbf{Model} & \textbf{OA} & \textbf{F1\_macro} & \textbf{F1\_weighted} \\ \hline
        Harmonic-14 & 0.904 (\(\pm\) 0.007) & 0.874 (\(\pm\) 0.011) & 0.905 (\(\pm\) 0.006) \\
        Emb-64 & 0.936 (\(\pm\) 0.008) & 0.917 (\(\pm\) 0.005) & 0.937 (\(\pm\) 0.007) \\
        Emb-Top14 & 0.924 (\(\pm\) 0.009) & 0.903 (\(\pm\) 0.006) & 0.926 (\(\pm\) 0.009) \\ \hline
    \end{tabular}
    \caption{National performance comparison under identical eco-region folds and weights. Values are mean (± sd) across CV folds.}
    \label{tab:national_ablation}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{lccc}
\hline
\textbf{Eco-region} & \textbf{Acc (Emb-64)} & \textbf{Acc (Emb-Top14)} & \textbf{Samples} \\ \hline
Greater Semi-Continental East & 0.967 & 0.960 & 2.87\,M \\
Oceanic Southwest & 0.959 & 0.953 & 2.66\,M \\
Semi-Oceanic North Centre & 0.966 & 0.958 & 2.46\,M \\
Central Massif & 0.935 & 0.927 & 1.93\,M \\
Mediterranean & 0.836 & 0.803 & 1.46\,M \\
Alps & 0.906 & 0.888 & 0.72\,M \\
Pyrenees & 0.965 & 0.947 & 0.56\,M \\
Greater Crystalline West & 0.946 & 0.931 & 0.49\,M \\
Vosges & 0.908 & 0.900 & 0.40\,M \\
Corsica & 0.694 & 0.662 & 0.35\,M \\
Jura & 0.936 & 0.920 & 0.20\,M \\ \hline
\end{tabular}
\caption{Eco-region accuracies for AlphaEarth embedding models (Emb-64, Emb-Top14), matching regions and sample counts in Table~\ref{tab:eco-region}.}
\label{tab:eco-region-emb}
\end{table}

>>>>

\begin{table}[H]
    \centering
    \begin{tabular}{lccc}
        \hline
        \textbf{Model} & \textbf{OA} & \textbf{F1\_macro} & \textbf{F1\_weighted} \\ \hline
        Harmonic-14 & 0.904 (\(\pm\) 0.007) & 0.874 (\(\pm\) 0.011) & 0.905 (\(\pm\) 0.006) \\
        Emb-64 & 0.936 (\(\pm\) 0.008) & 0.917 (\(\pm\) 0.005) & 0.937 (\(\pm\) 0.007) \\
        Emb-Top14 & [to fill] & [to fill] & [to fill] \\ \hline
    \end{tabular}
    \caption{National performance comparison under identical eco-region folds and weights. Values are mean (± sd) across CV folds.}
    \label{tab:national_ablation}
\end{table}

@@

\begin{table}[H]
\centering
\begin{tabular}{lccc}
\hline
\textbf{Eco-region} & \textbf{Acc (Emb-64)} & \textbf{Acc (Emb-Top14)} & \textbf{Samples} \\ \hline
Greater Semi-Continental East & 0.967 & [to fill] & 2.87\,M \\
Oceanic Southwest & 0.959 & [to fill] & 2.66\,M \\
Semi-Oceanic North Centre & 0.966 & [to fill] & 2.46\,M \\
Central Massif & 0.935 & [to fill] & 1.93\,M \\
Mediterranean & 0.836 & [to fill] & 1.46\,M \\
Alps & 0.906 & [to fill] & 0.72\,M \\
Pyrenees & 0.965 & [to fill] & 0.56\,M \\
Greater Crystalline West & 0.946 & [to fill] & 0.49\,M \\
Vosges & 0.908 & [to fill] & 0.40\,M \\
Corsica & 0.694 & [to fill] & 0.35\,M \\
Jura & 0.936 & [to fill] & 0.20\,M \\ \hline
\end{tabular}
\caption{Eco-region accuracies for AlphaEarth embedding models (Emb-64, Emb-Top14), matching regions and sample counts in Table~\ref{tab:eco-region}.}
\label{tab:eco-region-emb}
\end{table}
